Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
update code

\begin{lstlisting}
def aeval(e: Expr, env: Env, store: BStore, time: Time, cache: Cache, continue: Cont): Ans = {
  val config = Config(e, env, store, time)
  /* lookups the out cache, uses the values if contains this config */
  if (cache.outContains(config)) return continue(Ans(cache.outGet(config), cache))
  /* uses the values from in cache */
  val new_cache = cache.outUpdate(config, cache.inGet(config))
  val new_time = (e::time).take(k)
  e match {
    case Let(x, App(f, ae), e) =>
      val closures = atomicEval(f, env, store).asInstanceOf[Set[Clos]]
      nd[Clos, Ans](closures, Ans(Set[VS](), new_cache), { case (clos, Ans(acc, cache), closnd) =>
        ......
        aeval(body, new_env, new_store, new_time, cache, { case Ans(bodyvss, bodycache) =>
          nd[VS, Ans](bodyvss, Ans(Set[VS](), bodycache), { case (vs, Ans(acc_vss, cache), bdnd) =>
            ......
            aeval(e, new_env, new_store, time, cache, { case Ans(evss, ecache) => 
              bdnd(Ans(acc_vss ++ evss, ecache)) 
            })
          },
          { case Ans(evss, cache) => closnd(Ans(evss ++ acc, cache)) })
        })
      },
      /* updates the out cache after evaluation */
      { case Ans(vss, cache) => continue(Ans(vss, cache.outUpdate(config, vss))) })

>>>>

\begin{lstlisting}
def aeval(e: Expr, env: Env, store: BStore, time: Time, cache: Cache, continue: Cont): Ans = {
  val config = Config(e, env, store, time)
  /* lookups the out cache, uses the values if contains this config */
  if (cache.outContains(config)) return continue(Ans(cache.outGet(config), cache))
  /* uses the values from in cache */
  val new_cache = cache.outUpdate(config, cache.inGet(config))
  val new_time = (e::time).take(k)
  e match {
    case Let(x, App(f, ae), e) =>
      val closures = atomicEval(f, env, store).asInstanceOf[Set[Clos]]
      nd[Clos, Ans](closures, Ans(Set[VS](), new_cache), { case (clos, Ans(accouter, cache), closnd) =>
        ......
        aeval(body, new_env, new_store, new_time, cache, { case Ans(bodyvss, bodycache) =>
          nd[VS, Ans](bodyvss, Ans(Set[VS](), bodycache), { case (vs, Ans(acc_vss, cache), bdnd) =>
            ......
            aeval(e, new_env, new_store, time, cache, { case Ans(evss, ecache) => 
              bdnd(Ans(accinner ++ evss, ecache)) 
            })
          },
          { case Ans(evss, cache) => closnd(Ans(evss ++ accouter, cache)) })
        })
      },
      /* updates the out cache after evaluation */
      { case Ans(vss, cache) => continue(Ans(vss, cache.outUpdate(config, vss))) })
